Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Words.

The deployment we envision and have started to implement
uses a single paid App Engine instance, which is publicly known and usable by anyone.
Client software is configured to use this public instance by default.
A preconfigured public instance has great usability advantages
because there is nothing for the user to upload and nothing to configure.
The number of parties able to analyze users' traffic patterns is somewhat increased:
the path from user to Tor bridge now includes App Engine and the web app operators,
in addition to the ISP and intermediate routers that were there before.
On the other hand, the Tor bridge no longer gets to see users' IP addresses:
all it sees are many connections from the App Engine.
In effect, App Engine and the web app become what Tor calls a ``guard node,''
a privileged relay that takes the first hop in the chain of relays.
Because Tor is encrypted and integrity-protected, neither App Engine nor the app operators
are able to read or alter users' communications, but being on path enables them
to do things like measure packet timing patterns.

@@

The code that runs on App Engine is very simple.
It just statelessly copies HTTP requests and responses.
Another possible deployment scenario uses a PHP implementation of the reflector,
deployed on an ordinary web hosting service other than App Engine.
In this scenario, domain fronting is not used;
instead unblockability depends on there being many (individually blockable) PHP reflectors.
In other words, it is roughly the same situation as exists today with Tor bridges,
except that it can be much easier for a volunteer to upload a PHP file to a web host
than to set up Tor bridge or other proxy.
Such PHP bridges could potentially automatically report their own URLs,
which could be distributed using a system like BridgeDB.

>>>>

The deployment we envision and have started to implement
uses a single paid App Engine instance, which is publicly known and usable by anyone.
Client software is configured to use this public instance by default.
A preconfigured public instance has great usability advantages
because there is nothing for the user to upload and nothing to configure.
The number of parties able to analyze users' traffic patterns is somewhat increased:
the path from user to Tor bridge now includes App Engine and the web app operators,
in addition to the ISP and intermediate routers that were there before.
On the other hand, the Tor bridge no longer gets to see users' IP addresses:
all it sees are many connections from App Engine.
In effect, App Engine and the web app become what Tor calls a ``guard node,''
a privileged relay that takes the first hop in the chain of relays.
Because Tor is encrypted and integrity-protected, neither App Engine nor the app operators
are able to read or alter users' communications, but being on path enables them
to do things like measure packet timing patterns.

@@

The code that runs on App Engine is very simple.
It just statelessly copies HTTP requests and responses.
Another possible deployment scenario uses a PHP implementation of the reflector,
deployed on an ordinary web hosting service other than App Engine.
In this scenario, domain fronting is not used;
instead unblockability depends on there being many (individually blockable) PHP reflectors.
In other words, it is roughly the same situation as exists today with Tor bridges,
except that it can be much easier for a volunteer to upload a PHP file to a web host
than to set up Tor bridge.
Such PHP bridges could potentially automatically report their own URLs,
which could be distributed using a system like BridgeDB.
